---
title: "p8105_hw1_az2852"
output: github_document
---
# Question 1
```{r data}
data("penguins", package = "palmerpenguins")
```

```{r libraries, message = FALSE, echo = FALSE}
library(tidyverse)
```

The penguins (344 rows × 8 columns) dataset contains flipper, bill, and body mass data for Adelie, Gentoo, and Chinstrap penguins recorded in 2007-2009 from Torgersen Island, Biscoe Island, and Dream Island. Each row is data for one penguin, including bill length, bill width, and flipper length in centimeters, and body mass in grams. The average flipper length for the penguins in the dataset is `mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`

Below is a plot of flipper length agains bill length for the penguins in the dataset (342 penguins and 2 missing values). Penguins of the same species tend to have similar bill length and flipper length. The data is clearly clustered by species with just a few overlapping points. It appears that the Adelies have the shortest flippers and bills. The Chinstraps have the longest flippers. The Gentoos have the longest bills. It also appears that penguins with longer flippers tend to have a longer bill.
```{r scatterplot, warning=FALSE}
ggplot(penguins, aes(
  x = bill_length_mm,
  y = flipper_length_mm, 
  color = species)) + 
  geom_point()+
  labs(x = "Flipper Length (mm)", 
       y = "Bill Length (mm)" 
)
```